---
title: "shiny app and reproducible research pitch"
author: "Sylvia Nunez"
date: "`r Sys.Date()`"
output: 
  ioslides_presentation: 
    keep_md: yes
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny Presentation
Instructions:
Your Reproducible Pitch Presentation
OK, you've made your shiny app, now it's time to make your pitch. You get 5 slides (inclusive of the title slide)  to pitch a your app. You're going to create a web page using Slidify or Rstudio Presenter with an html5 slide deck.
Here's what you need
5 slides to pitch our idea done in Slidify or Rstudio Presenter
Your presentation pushed to github or Rpubs
A link to your github or Rpubs presentation pasted into the provided text box
Your presentation must satisfy the following
It must be done in Slidify or Rstudio Presenter
It must be 5 pages
It must be hosted on github or Rpubs
It must contained some embedded R code that gets run when slidifying the document




## Interactive Plot

```{r eruptions}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "orange")
})
```


## R Output

```{r cars}
summary(cars)
```
## Thanks 


